Quantum Computing and its Implications on Digital Security

### 2021-12-16 paper.tex
fix: Typo

\begin{abstract}
Quantum computing has been gaining more and more relevance in the last couple of years and is often rather seen as a thread than a blessing by society. This paper aims to inform readers about the topic on a high-level to join the discussion about the future relevance of quantum computing. First, this paper will explain the basics of quantum computing and dive into types of quantum computers including ion traps, nuclear magnetic resonance quantum computers and quantum computers based on josephson junctions. Afterwards, the effects of quantum computing algorithms, especially Shor's and Grover's algorithm on current security mechanisms are discussed, rounding off by explaining approaches on how to achieve post quantum security.
\end{abstract}

>>>>

\begin{abstract}
Quantum computing has been gaining more and more relevance in the last couple of years and is often rather seen as a threat than a blessing by society. This paper aims to inform readers about the topic on a high-level to join the discussion about the future relevance of quantum computing. First, this paper will explain the basics of quantum computing and dive into types of quantum computers including ion traps, nuclear magnetic resonance quantum computers and quantum computers based on josephson junctions. Afterwards, the effects of quantum computing algorithms, especially Shor's and Grover's algorithm on current security mechanisms are discussed, rounding off by explaining approaches on how to achieve post quantum security.
\end{abstract}
